\chapter{Introduction}
\label{chap:intro}
%http://thesistips.wordpress.com/2012/03/25/how-to-write-your-introduction-abstract-and-summary/

% It introduces the problem and motivation for the study.

% - Tell the reader what the topic of the report is.
% - Explain why this topic is important or relevant.

% It provides a brief summary of previous engineering and/or scientific work on the topic.
% - Here you present an overview what is known about the problem.  You would typically cite earlier studies conducted on the same topic and/or at this same site, and in doing so, you should reveal the yawning void in the knowledge that your brilliant research will fill.

% It outlines the purpose and specific objectives of the project.
Development of an online multiplayer game serving many users can be split into two parts: Creating the explicit game functionality, and creating the underlying architecture. When developing new games this is often mixed together as the underlying architecture is only used for the specific game. This gives the developer the opportunity to write an extremely game specific architecture. Sometimes the developer want to create other similar games with the same underlying structure as previous games - but as the architecture and the game itself is intertwined, it is hard to reuse the same structure.
The focus of this project is on creating a flexible and reliable server architecture \fxfatal{client-server? smth else?} allowing easy development of multiplayer games for smartphones. The aim is to make it possible for developers to focus on the game development without having to worry about managing the underlying architecture. 

The framework will focus on creating a platform for multiplayer location-based games. The framework have to be scalable meaning the server can easily handle different devices. This means it is a requirement that multiple clients to connect to the server and take different actions at the same time. There is a focus on creating a thread based server framework - which handles actions individually. The framework will have the functionality of handling GPS-coordinates and based on it take some sort of action, depending on the game implementation. 

Creating new games from scratch requires time and while some firms might have time and funds enough to create everything themselves, it is always a good thing to use less time on the same product. The extra time either means a bigger surplus for the developer or more time to work on the game features. If a developer needs to create a game with the same basic functionality as a previous model - he will as mentioned have to first search through the previous model and extract wanted features and exclude unwanted. This does require extra time compared to having the framework completely accessible however the functionality of the framework might not be an exact match to what you need in your game which also requires extra time to adjust to. We argue creating a precise but flexible framework saves more work and time from recreating code, than code it requires having to adjust to it.

A big problem for developers of a new game and working with an existing framework, is as mentioned to fit it for their specific needs. A framework is the basic set of functionality and structural guidelines for the game to be built upon. Overall game development rarely fits typical software life cycle methods such as the waterfall method - but fairly an agile development process is used\cite{Gamedevelopment}. This results in the functionality might have to change on a frequent basis. Whether this means new functionality or rewriting already existing functions - a game with intertwined framework and game will take more time to rewrite. Consider a third person shooter game, if you built functionality around the specific gun types and their attributes and you far into the development need to implement another gun type. The developer would have to rewrite all the code revolved around the specific gun type to suddenly include the new gun type. This requires a lot of extra time compared to having a framework that allows fluent adding and removing gun types. Not to mention examples where you have to abandon an idea and create something entirely different - instead of having to rewrite all of the code the developer have a framework which is still independent of the game itself.

The size and the amount of divisions of a developing firm also matters. The more different people working on it, the more precision is needed either in the documentation or the framework. Having multiple people writing code on the same game requires the underlying architecture to be as steady and consistent as possible. Changing something in the framework or the underlying architecture requires a notification to all different divisions and people working on the game and might result in some code refactoring \cite{Gameprod}. These firms often create their own framework and document it through the Game design document \cite{Gamedesign} in order for it to fit exactly their needs. This causes them to have a consistent and steady framework to work upon - and work individually without consulting different divisions. Smaller developers might not have the luxury of creating a completely game specific framework for each of their projects. This results in smaller developers often have to spent more work hours adjusting their code to what their co-developers have coded.

Another problem with developing different games from scratch as opposed to having a standardized framework is the compatibility. Having different types of devices with different versions of various operating systems means that some devices might not be compatible with the desired program. What this means is that programs act differently on different devices - and with an existing framework this only have to be implemented once. Having a framework that is already compatible with the different devices allows the coder to focus solely on the game and therefore limiting the amount of time needed for coding versatile code.

Constructing a framework that could be used by different developers could save the developer a lot of time and money, given the developer uses the framework as intended. It could and should be easier to use for the developer - giving him less work hours needed to create the same content he otherwise would. The struggle with creating a framework like this is that it has to be flexible enough for game developers to create diverse games, but still be precise enough to not having to create an immense amount of code in order to fit it to your game to it.

The subject is widely pursued in the form of game engines and general APIs. A large amount of games being developed are developed on an already existing game engines. An example of a game engine is the `Adventure Game Studio' and this is one of the biggest APIs for creating games in third person pre-rendering. The developer `Chris Jones' have created different functionality he deemed important for creating these games and published it in the form of an simple IDE for game developers \cite{adv-game}. It is really specific in the way its focused on third person adventure games - making really specific functionality.
Another example of game engines is full blown engines with multiple purposes for a specific genre. One of the most used engines for first person shooters is the `Unreal Engine' - which is used for almost every major shooter or fighter game. It is used both as visual aid providing 3D rendering, but also gives pre-rendering functionality.

% It provides a ‘road map’ for the rest of the report.
% - This is so that the reader knows what’s coming and sees the logic of your organization.
% - Describe (in approximately one sentence each) the contents of each of the report/thesis chapters.

\input{indhold/introduktion/problemformulering}
\input{indhold/introduktion/chapterdescription}
