\section{Problem Statement}
\label{sec:probstate}
When creating games time and money are valuable resource. To ensure a high amount of quality code, the developer has to spent a lot of time writing code that could be found in a generic framework, increasing the cost unnecessarily. This naturally raises the question:

%\mbox{\parbox[b][2.5cm][c]{0.95\textwidth}{\textit{How can we develop a framework for creating multiplayer games - increasing the experience for the developers.}}}

\mbox{\parbox[b][2.5cm][c]{0.95\textwidth}{\textit{How can a flexible framework for creating multiplayer games be developed.}}}\fxfatal{Bør stadig overvejes!}

\noindent The idea is simple: we want to create a framework for creating simple location-based multiplayer shooter games. In order to properly answer the stated problem, these goals should be fulfilled:

\paragraph{Flexibility} The framework has to be as flexible as possible. I.e., it should allow implementation of as broad a spectrum of games as possible within the mentioned genre.
\paragraph{Scalability} The framework should be able to handle multiple games, each with multiple users. The purpose of hosting several games at once is to allow development of relatively short games with a limited number of players each, e.g. a group of friends.
\paragraph{Ease of Use} The framework has to be easy to use for developers. If it is too complicated it will not be as attractive to start using - the idea is to make development easier rather than harder.





%Scenarios
%\input{indhold/sce1}
%\input{indhold/sce2}
%\input{indhold/sce3}

%In order to do so several approaches are available.

%A simple approach is to measure the signal strength of the device and use that as the base for predicting when connection will be unavailable. Using this method a stable but slowly dropping signal strength might indicate a future with no connection available, in this event the required web resources should be cached so they are available doing an offline period. Another scenario could when the signal is unstable but the average remains high, this could indicate interference in the area but no risk of a significant offline period, in this case caching is not necessary.
%
%Another approach is to base the prediction on historical data of the near area. This can be done by gathering data of where Internet connections usually drops and build a map for the available providers. Then the caching will be done when a device is predicted to move into such an area.

%Problem statement
% How can a user be guaranteed to always have relevant information available, regardless of network connectivity?