\chapter{Problem Analysis}

%% Problem
%  Define the problem in terms of:

%  - Problem area / General problem
%  - People affected
%  - Problem results in...
%  - What is gained from solving it?
Development of an online multiplayer game serving many users can be split into two parts: Creating the game, and creating the underlying architecture. The focus of this project is on creating a flexible and reliable server architecture \fxfatal{client-server? smth else?} allowing easy development of multiplayer games for Android smartphones. The aim is to make it possible for developers to focus on the game development without having to worry about managing the underlying architecture. 

The main problem for developers of a new game is the issue of having to creating good usable framework for their specific needs. A framework is a basic set of functionality and structural guidelines for the game to be built upon. At the start of a project, game developers set out to create a framework that can handle all of the functions that the game need, without really having specified precisely how those functions are implemented. This means that if functions change or an entirely new functionality need comes up, the framework have to be adjusted to the specific need. An example of this could be how the game handles several users, maybe the game have different needs depending on some variating variable. The amount of workload a developer has to put into creating the framework to match exactly his demand is greatly increased. The different requirements and often change in the framework often makes code incomprehensible.

It requires a lot more work and overview from the small game developers to keep the framework completely up to date. Bigger firms almost always require multiple sections to use the same framework\fxwarning{kilde?} - and therefor consistency (in form of little to no change) is a must. More often than not these firms create their own frameworks to design them exactly the way they need it, but smaller firms might have limited funds or time. This means that smaller developers often either skip on creating features they normally would or create sloppy and inefficient code as a side effect.

Creating a joint framework that could be used by different developers could save smaller and new game developers a lot of time, and create a standard that makes coding on top of it easy. 

A problem with developing different games from scratch as opposed to having a standardized framework is the compatibility. Having different types of devices with different versions of various operating systems means that some devices might not be compatible with the desired program. What this means is that programs act differently on different devices because of the inconsistent code - and for this to be a non issue you would have to create code to match each type of device and operating system which is an extreme task. Having a framework that is already compatible with the different devices allows the coder to focus solely on the game.

The subject is widely pursued in the form of game engines. A large amount of games being developed are developed on an already existing game engines. An example of a game engine is the `Adventure Game Studio' and this is one of the biggest frameworks for creating games in third person pre-rendering. The developer `Chris Jones' have created different functionality he deemed important for creating these games and published it in the form of an simple IDE for inexperienced game developers \cite{adv-game}. Another example of game engines is full blown engines with multiple purposes for a specific purpose. One of the most used engines for first person shooters is the `Unreal Engine' - which is used for almost every major shooter game.






%% Potential problems
%  Server related:
%  - Network connection
%  - Efficient communication
%  - Many users
%  - GPS, latency (actions close to each other?)

%  Non server related:
%  - Attracting users
%  - Keeping users
%  - Earning money
%  - Similar applications to learn from

%% Constraints
%  Which contraints are there in regards to this project?
