\subsection{Server Architecture}
\label{sec:server}

The server is structured in three layers: a dispatcher service, a logic layer and a data layer. This is based on MVC Model described in \Cref{sec:mvc}. Because we wanted to develop a framework for creating future location-based games, we had to make a decision how to achieve this goal. We could not interleave framework-specific functionality with the specific game we developed along side our framework. The result was these three layers. We wanted to build a communication layer to handle the interface between the client and the server and a data layer to handle the interface between the server and the database. These two layers were chosen rather intuitively early in the design process. Our next choice was how to choose a way to implement a specific game capable of using the framework, while still being scalable and encapsulated. We decided to make the threaded class called Game Thread handle all game-specific calculations, logics and responses. 
It was helpful to build a game alongside the framework, this helped us to figure out the need for a service to handle timed events in the framework, which resulted in the Event Timer. We also discovered the need for unit to handle client requests that requested functionality prior to the Game Thread. This was requests like logging in, and seeing all active games, which cannot be handled by a game thread yet since it might not be created yet. The result was the Admin. The Event Timer and the Admin are both positioned in the Logic Layer, because they help make logical decisions based on requests made by the client. 

%Server Architecture
\input{indhold/theframework/DesignServer/serverarchitecture}

%Dispatcher Service
\subsection{Dispatcher Service}
This layer is responsible for communication between client and server, this responsibility is divided between an IO module and a Dispatcher. In this section we will first examine Synchronous and Asynchronous IO in order to determine which is best suited for this framework and then the Dispatcher which forwards messages to the Logic Layer. We decided on Asynchronous IO and base our design on \cite{subsubsec:sync}.	 %http://msdn.microsoft.com/en-us/library/fx6588te%28v=vs.110%29.aspx

The Asynchronous IO unit is handling socket creation and TCP/IP communication, a rather trivial part of a client-server interface when you disregard the communication type. The need for out Dispatcher unit has been revealed by building our game. We need a way to dispatch requests from the client to the right component and method on the server. We dispatch to either Admin or Game Thread, by reading the request from the client and determine what type of request it is and continue accordingly. We decided to build the Dispatcher to encapsulate reading and analysing the requests from the client. Alternatively, we could have handed everything to Admin and incorporated the Dispatcher's functionality into the Admin, but we did not consider this a well structured framework.

\input{indhold/theframework/DesignServer/blockingvsnonblocking}
\input{indhold/theframework/DesignServer/dispatcher}

%Logic Layer
\subsection{Logic Layer}
This layer parses and reacts to the messages received from the Dispatcher. The logic layer interact with the Game Threads and consists of the Event Timer module which is callable from the Game Threads and can do a callback at a later time. The layer also contains the Admin module responsible for creating Game threads as well as non-game specifics such as authenticating logins.

The framework allows the user to use services like logging a client in through an XML-based interface. Services in the framework requires the user to implement proper XML-based communication on the client-side. A discussion about the use of XML seen in \ref{subsec:interfaces}. The framework also offers to handle Game Events, timed to occur after a specified time-stamp. This service used by creating a Game Event in the Game Thread being build by the user of the framework. We decided to build the Event Timer this way to encapsulate time-handling, and make a generic module that can be used for many different events. The user of the framework can specify what should happen for a given event in the Game Event class.

\input{indhold/theframework/DesignServer/admin}
\input{indhold/theframework/DesignServer/eventtimer}

%Game Block
\subsection{Game Block}
This is the workstation of the user of the framework. This block interacts with all the layers in the framework and makes use of the functionality provided by the framework. This class encapsulates all game-specific logic.

This is where we designed the framework to allow the user to develop a game. The framework has several rules the user has to follow when using the framework. They are explained for each module in the design. An example is the XML communication from client to server.
 
\input{indhold/theframework/DesignServer/gamethread}

%Data Layer
\subsection{Data Layer}
The data layer provides the user of the framework with the functionality to store data for later use. It is developed in a location-based game-format, as it was developed alongside our game.

\input{indhold/theframework/DesignServer/databasedesign}

